Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-05 anzjs2018/sections/04_implementation.tex
Update captions

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_timing.pdf}
    \caption{
        Application timings were recorded for each component of each
        iteration, and averages over a 15~minute window are shown here.
        The timings shown are \emph{wall time}, the actual time passed,
        not CPU time.
        Steps that only involve particle calculations are approximately
        of complexity $O(N)$,
        however some steps are a little more complex (writing ETAs involves computing quantiles), 
        so there is a slightly exponential trend.
    }
        % The timings for various parts of the application, and overall. %
        % The trend is slightly non-linear due to the complexity of the ETA generation step, %
        % which requires sorting of the particle ETAs to obtain quantile estimates.}
    \label{fig:timings}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_dist.pdf}
    \caption{
        The distance between the observation and the nearest point on the shape
        is calculated by finding the shortest distance between point and path.
        This gives an approximate idea of GPS error, however it should be noted
        that many observations are made automatically at way points,
        which accounts for the peak at 1m.
        Note also that these observations have been truncated at 20m.
    }
    \label{fig:dist_to_route}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/04_model_results_neff.pdf}
    \caption{
        The effective sample size is an approximate measure of the variance
        of the particle weights.
        When all particles have equal weights, $N_\text{eff} = N$,
        while if all the weight is on one particle, $N_\text{eff} = 1$. 
        The figure is subset by system noise, which shows how $N_\text{eff}$ 
        decreases as system noise increases,
        while increasing GPS error (on the $x$-axis) increases $N_\text{eff}$.
        Increasing $N$ has a negative effect on $N_\text{eff}$ but this is
        only evident when $N_\text{eff}$ is larger.
        The error bars show $\pm 2$SE.
    }
    \label{fig:perf_stats}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/04_model_results_times.pdf}
    \caption{
        The variability of travel time within a segment increases with GPS error,
        and decreases slightly with increasing number of particles.
        There is no visible effect of system noise on travel time variability.
        The error bars show $\pm 2$SE.
    }
    \label{fig:travel_times}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_timing.pdf}
    \caption{
        The average real-time running time of each step within each iteration
        over a 15~minute off-peak window.
        The vehicle update and writing ETA steps involve sorting the particles,
        which is an operation of $\mathcal{O}(N\log N)$ complexity.
        Total time is for the entire iteration, which includes fetching the data from the API.
        % Total time increases as the number of particles $N$ increases.
        % The reason for the large contribution of writing ETAs is that
        % this step involves estimation of quantiles,
        % which requires sorting the particles, 
        % The vehicle update step also involves sorting whenever the sample
        % degenerations and resampling is required.
        % Total time also includes fetching the data from the API,
        % which is constant for any $N$, which explains the increase
        % in standardised total time for $N=500$.
    }
    \label{fig:timings}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_dist.pdf}
    \caption{
        The distribution of minimum distance between observed vehicle location
        and the route path, truncated to 20~meters.
    }
    \label{fig:dist_to_route}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/04_model_results_neff.pdf}
    \caption{
        The effective sample size, $N_\text{eff}$,
        and degeneration rate for varying values of GPS error,
        system noise, and number of particles $N$.
        % increases with GPS error and decreases with system noise,
        % however both effects are reduced for larger $N$.
        % Conversely, degeneration rate decreases with GPS error and
        % system noise, although the effect of the latter is very small,
        % and again the relationship is less pronounced for larger $N$.
    }
    \label{fig:perf_stats}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/04_model_results_times.pdf}
    \caption{
        The relative variability of travel time estimates for varying
        values of GPS error, system noise, and number of particles, $N$,
        with error bars $\pm 2$ standard errors.
        % as GPS error increases,
        % with no clear relationship with system noise.
        % Increasing $N$ decreases variability.
    }
    \label{fig:travel_times}
\end{figure}
